### 2021-07-11 doc/thesis/chapters/system-architecture-and-concept.tex
system concept text

@@

%%%%%%%%%%%%%%%%%%%%
\section{Block Diagram}

%%%%%%%%%%%%%%%%%%%%
\subsection{describe blocks}

>>>>

\noindent
A very high-level overview of the entire system is given by the block diagram in Fig.\ref{fig:bd_system_overview_highlevel}.
It shows the front end, which processes the received antenna signal, so that it can be used in the FM radio receiver block.
The radio receiver itself is implemented in multiple different variants.
The produced audio output is sent to a speaker, since the ultimate goal is to listen to a radio stations' audio signal.

\includepicture [1.0] [0] [H] {High-level overview of the system.} {bd_system_overview_highlevel} {img/draw.io/bd_system_overview_highlevel}

@@

%%%%%%%%%%%%%%%%%%%%
\section{System concept}

The overall system concept has to be developed in a way, to fit the respective projects' needs and requirements.
There should be a clear structure, in order to help to create a working system successfully.
This structure should include a description of the data source, the data processing blocks and stages, commonly used parameters, as well as a strategy to verify the correct functionality of the system.
A good system structure tries to share as many parts as possible in the system.
This is to minimize the points of failure, as well as to reduce the effort of implementation.

In the apparent projects' case, a single block of the system is implemented in multiple ways, which should however, all compute an equal output.
Thus, it is of advantage to define the data source to be common for all of these variants, to create a unified situation at the input.
This significantly eases the verification of the functionality in the final step, since all variants are expected to create the same output in the optimum, fully functioning case.
Not only the data source is important to be common, but also the way of verification.
In order to achieve that, the verification block needs to be able to compare multiple data outputs with the verification data, which is chosen to serve as the reference.\\

An example of a system concept and its architecture is shown in Fig.\ref{fig:bd_system_overview_detailed}.
Here, a common data source is provided by the block called \textit{Front End}.
It delivers data, that the \textit{FM Radio Receiver} block requires at its input.
Within this block, all the different implementation variants are shown in parallel.
They all work on this common input source and generate their respective output.
This output is written to a file.
Hereby, it is important to note, that the output of the \textit{Matlab} implementation is chosen to be the reference model of 'correct output'.
Its output is used as the verification data.
This is because Matlab was used to research decoding algorithms and to develop the DSP chain, which is used in the GNU Radio, HLS and VHDL implementations.
In addition to the verification data, the Matlab model also writes common parameters to a file.
These parameters are directly used in the other implementations, to ensure a common setup.
The final block, is the \textit{Verification} entity, which compares the output of all the respective variants, with respective to the chosen model parameters.

A major point in this system concept is, that it works independently of the respective implementation methodology.
This is especially important, since there is no possible way to run all these different variants in a single verification environment.
Instead, each methodology writes an output file, which is a functionality that is available anywhere.

\includepicture [1.0] [0] {Block diagram of the overall system concept.} {bd_system_overview_detailed} {img/draw.io/bd_system_overview_detailed}
